Analyzing the impact of social attributes on commit integration success

### 2017-03-25 Paper/MSRChallenge2017.tex
several todos addressed

\textbf{Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?}

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience. If we were unable to find information about an author than we
assigned the commit empty values for these factors.
We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project.

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We train and present results for both
data sets individually.
\section{Evaluation}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

>>>>

\textbf{Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions of 
the developer's build success
than only using technical data?}

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience. If we were unable to find information about an author than we
assigned the commit empty values for these factors.
We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project. These values were investigated to understand and be able to quantify the developers’ experience.

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling. We downsampled the entire dataset being analyzed and then performed cross-validation on it. Since the cross-validation is stratified, the proportion of 50-50 is maintained through the training and testing folds. We train and present results for both
data sets individually in Sections \ref{eval}A, \ref{eval}B and \ref{eval}C.
\section{Evaluation} \label{eval}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\
